Widely separated, comoving stars in \textsl{Gaia DR1}

### 2016-09-29 paper/ms.tex
title, abstract, keywords

\title{Wide binaries in Gaia DR1}
\author{People}

@@

\begin{abstract}
Blerg.
% Context
% Aims
% Methods
% Results
\end{abstract}

\keywords{
  methods: data analysis
  ---
  methods: statistical
}

>>>>

\title{Widely separated, comoving stars in \textsl{Gaia DR1}}
\author{APW, SO, DWH, DNS, DSTN, others}

@@

\begin{abstract}
% Context
The primary sample of the \gaia\ \textsl{First Data Release} is the brand-new
\textsl{Tycho-Gaia Astrometric Solution}. The precision and size of this sample
creates an opportunity to find new binary stars and moving groups, especially
rare binaries or sparsely populated groups.
% Aims
Here we seize this opportunity.
% Methods
We use a justified marginalized likelihood ratio test to separate
pairs of stars with surprisingly similar three-space velocities from
those consistent with being drawn from the field population.  Although
we perform some visualizations using a (bias-corrected) inverse
parallax as a distance, the likelihood test works in the observable
space and uses the \gaia\ noise model responsibly.
% Results
We find pairs of comoving stars in abundance out to very wide
separations, including separations of a few parsec! There does not
seem to be any tidal-disruption feature in the separation distribution
at sub-parsec scales. Pairs at separations beyond a
parsec---whether they are bound in a multiple system or drifting
apart---must be very short-lived. The photometric properties of the
members of these pairs are consistent with youth. The prospects for
testing stellar models and chemical abundance measurements are
superficially discussed.
\end{abstract}

\keywords{
  binaries: visual
  ---
  methods: statistical
  ---
  open clusters and associations: general
  ---
  parallaxes
  ---
  proper motions
  ---
  stars: formation
}
